Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-11 paper/paper.tex
Some changes to Sec 5

Having constrained only 3 parameters, one might wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Even if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3, as the results for the classification tree example in Figure
\ref{fig:tree} shows.

We cannot discard that another region of parameter space
could also work.
It might be interesting to explore in the
future with a higher sampling of the parameter space once new 
observations  clarify the kinematic nature of \tol \footnote{In
  Section \S \ref{sec:conclusions} we describe  in more detail what
  kind of observations could be performed in the near future to
  improve our understanding of \tol's kinematics.}.
Furthermore, considering the sparse sampling of parameter space and the results
from the random forest classifier, it is safer to consider that
the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
  cl}$ are actually lower/upper/lower bounds, respectively.

@@

Which model has more
chances to be correct?  
We discard the rotation model by considering that the rotational
velocity of $\sim350$ \kms\ is too high for such a low
mass system. 
\tol's inferred rotational velocity is larger than the
Milky Way's ($\sim200$\kms) while its baryonic mass is one order
of magnitude smaller. 
Furthermore, \tol's structural properties seem to be similar to known dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
\tol. 
These dE galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This leads us to prefer the multiphase model as it provides 
a broad consistency with kinematic properties of dE galaxies.

@@

Another observational hint to clarify \tol's state could be
the measurement of the \lya ionizing continuum escape fraction. 
The multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle, i.e. some sightlines can have
an escape fraction close to $100\%$, \citep{Gronke2016}.

>>>>

Having constrained only 3 parameters, one might wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading because merely the best-fit values of (some of) those $3$ parameters, i.e., the corresponding constraint to a given sub-region in the parameter space, make the other parameters less important.
For instance, in our case the large value of $P_{\rm cl}$ makes radiative transfer effects, and therefore other parameters such as the clump column density less relevant for the emergent line profile. However, for instance larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce additional radiative transfer effects and thus increase the number of relevant parameters \citep[see ][for details]{2017arXiv170406278G}. 
This means that even
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected,
\mg{I am not sure I understand the rest of this sentence. What do you mean there?}
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3, as the results for the classification tree example in Figure
\ref{fig:tree} shows.

We cannot discard that another region of parameter space
could also yield a good fit to the observed line-profile.
This might be interesting to explore in the
future with, e.g., a higher sampling of the parameter space once new 
observations  clarify the kinematic nature of \tol \footnote{In
  Section \S \ref{sec:conclusions} we describe  in more detail what
  kind of observations could be performed in the near future to
  improve our understanding of \tol's kinematics.}.
Furthermore, considering the sparse sampling of parameter space and the results
from the random forest classifier, it is safer to consider that
the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
  cl}$ are actually lower/upper/lower bounds, respectively.
\mg{This is interesting. Why do you think that? Could we use that to increase the quoted errors? I am worried that the referee will complain about the small errors.}

@@

Which model has more
chances to be correct?  
We discard the rotation model by considering that the rotational
velocity of $\sim350$ \kms\ is too high for such a low
mass system.  \mg{I am confused -- are much lower rotational velocities not exclude by the priors used?}
\tol's inferred rotational velocity is larger than the
Milky Way's ($\sim200$\kms) while its baryonic mass is one order
of magnitude smaller. 
Furthermore, \tol's structural properties seem to be similar to known dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
\tol. 
These dE galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This leads us to prefer the multiphase model as it provides 
a broad consistency with kinematic properties of dE galaxies.

@@

Another observational hint to clarify \tol's state could be
the measurement of the \lya ionizing continuum escape fraction. 
The multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle, i.e. some sightlines can have
an escape fraction close to $100\%$ \citep{Gronke2016}.
